Article Title

### 2013-08-15 sections/Theory.tex
minor

\subsection{Loss function}
The optimization of a covariance matrix estimate $\hat\Sigma$ is performed with respect to a \emph{loss function} $\mathcal L(\hat\Sigma,\Sigma)$, which expresses the discrepancy between $\hat\Sigma$ and $\Sigma$ and attains its minimum when $\hat\Sigma=\Sigma$.  
Then \emph{excess loss}  
\begin{equation}
\ell(\hat\Sigma,\Sigma) = \mathcal L(\hat\Sigma,\Sigma)-\mathcal L(\Sigma,\Sigma)
\end{equation}
assumes zero at its minimum.

@@

\subsection{Regularized estimators}

\emph{Regularization} is the deliberate biasing of the unbiased estimate toward a less variable low-dimensional \emph{target estimate} $\hat T$ in order to strike a favorable balance between bias and variance and minimize the estimator risk.  A regularized covariance matrix estimator must solve two problems: (a) choose and fit the target covariate estimate $\hat T$ and (b) mix $\hat\Sigma_0$ with $\hat T$ by the optimal amount. Regularized covariance matrix estimates can be generally expressed as 
\begin{equation}
\hat\Sigma_{d,\lambda} = mix(\Sigma_0,\hat T_{\hat d},\hat\lambda) 
\end{equation}
where $\hat d$ indicates the choice of the target estimate from the family of target estimates $T_d$ and $\hat \lambda$ regulates the amount biasing of $\hat\Sigma_0$ toward $\hat T$.
Both $\hat d$ and $\hat \lambda$ must be calculated from the training sample.

>>>>

\subsection{Loss functions and risk}
The optimization of a covariance matrix estimate $\hat\Sigma$ is performed with respect to a \emph{loss function} $\mathcal L(\hat\Sigma,\Sigma)$, which expresses the discrepancy between $\hat\Sigma$ and $\Sigma$ and attains its minimum when $\hat\Sigma=\Sigma$.  
Then \emph{excess loss}  
\begin{equation}
\ell(\hat\Sigma,\Sigma) = \mathcal L(\hat\Sigma,\Sigma)-\mathcal L(\Sigma,\Sigma)
\end{equation}
assumes zero at its minimum.

@@

\subsection{Regularization}

\emph{Regularization} is the deliberate biasing of the unbiased estimate toward a less variable low-dimensional \emph{target estimate} $\hat T$ in order to minimize the estimator risk by striking a favorable balance between bias and variance.
A regularized covariance matrix estimator must solve two problems: (a) choose and fit the target covariate estimate $\hat T$ and (b) mix $\hat\Sigma_0$ with $\hat T$ by the optimal amount. 
Regularized covariance matrix estimates can be generally expressed as 
\begin{equation}
\hat\Sigma_{d,\lambda} = mix(\Sigma_0,\hat T_{\hat d},\hat\lambda) 
\end{equation}
where $\hat d$ indicates the choice of the target estimate from the family of target estimates $\hat T_d$. $mix(\cdot,\cdot,\hat\lambda)$ is the mixing function of $\hat\Sigma_0$ and $\hat T_{\hat d}$ in proportion controlled by $\hat \lambda$. Both $\hat d$ and $\hat \lambda$ must be calculated from the training sample.

A number of regularization schemes have been developed, which differ by their target estimates and mixing functions.  In this study, we evaluate four regularized estimators.
